### 2016-08-05 Engine.tex
再次修改 verification 和 自适应节点部分

As stated in the filtering phase, once a suspicious position in the
text has been detected by the filter module, the verification module
checks that position for real pattern occurrences. Specifically, for
such a suspicious position $i$, the engine searches a sequence of
substrings of the text, where the first substring starts at $i$, in
the corresponding nodes in AMT from the root. If the text successfully
matched a key that is marked as a pattern end in some node, a pattern
is declared to be found at position $i$. However, if there is a
mismatch or the searching goes beyond the leaves of AMT, the engine
immediately forwards to the next position $i+1$ and invokes the
filter.

The pseudocode of the verification procedure is shown in Algorithm
\ref{alg:matching}. Suppose $i$ is a suspicious position in the
text. The $m\_len$ is the total length of the successfully matched
sub-strings of the text. The $node$ points to the current matching
node in the AMT. In addition, since all the keys in a node have the
same length, the notation $key\_len(node)$ is used to denote the
length of the keys in $node$.

@@

For the suspicious position $i$, the \textbf{while} loop from line 5
to line 11 checks whether there are patterns starting at $i$. The
checking starts form the root of AMT: if the corresponding sub-string
$T[i+m\_len, \, key\_len(node)]$ matches some $key$ in the current
$node$, the totally matched length $m\_len$ is increased by the length
of the key. At the same time, if the matched $key$ is also marked as a
pattern end, the engine will report that a pattern, which is
$T[i,\,m\_len]$, is found at position $i$. Then the matching transfers
to the child of $node.key$ and makes that child node to be the current
node. Once there is a mismatch or the current node goes beyond the
leaves of AMT (i.e.  $node = NULL$), the verification terminates, and
the engine forwards to the next position $i+1$.

@@

Next, an example is given in figure \ref{fig:matching} to illuminate
the verification for position $i$ of a given text string $T$, using
the AMT built in section \ref{subsec:amt}. The verification starts
from the root of AMT: according to $key\_len(root)=2$, the same length
sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
taken to check whether it's one of the keys in root. The result is:
$aa \in root$, and $aa$ is also marked as a pattern end. Therefore the
pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is found at position
$i$. Then the verification transfers to $node_1$, which is the child
node of $root.aa$.

At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
$T[i+2,\,6]=e^6$, which follows $T[i,\,2]$, is trying to match with
some key in $node_1$. The result is that: $e^6 \in node_1$ but it is
not a pattern end. Then the verification simply transfers to $node_5$,
which is the child of $node_1.e^6$.

At $node_5$, since the next sub-string $T[i+8,\,5]=u^5 \in node_5$ and
$u^5$ is marked as a pattern end, another pattern
$T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
$i$. Then the verification goes to the child of $node_5.u^5$, i.e.
$node_{10}$.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/Maps}
  \caption{The four sub-types of character maps. The triangles
    represent the corresponding child nodes.}
  \label{fig:character map}
\end{figure}

Figure \ref{fig:character map} illustrates the four sub-types of
character maps which are named according to their maximum
capacity. Instead of using an array of (\emph{key, child pointer})
pairs, the key part and the child pointer part are stored in the
separate arrays, which is able to keep the node structure compact
while supporting efficient search.

\begin{itemize}
\item \textbf{Map 4} (for $1 \leq ndp \leq 4$): The smallest map type
  can store up to 4 keys. It uses an array of 4 entries for keys and
  another array of the same length for child pointers. The keys and
  child pointers are stored at corresponding positions in their
  arrays, and the keys are sorted according to their ACSII
  values. Once the target string (character) is found in the key
  array, its child pointer can be located through the same position in
  the pointer array. Figure \ref{fig:character map} (a) shows a Map 4
  structure with three keys: $f$, $n$ and $p$, where the triangles
  with the keys inside represent the corresponding child nodes.

@@

\item \textbf{Map 256} (for $49 \leq ndp \leq 256$): The largest map
  type is simply an array of 256 child pointers with each pointer
  initialized to $NULL$. It is used for storing 49 to 256 keys.  In
  this kind of character map, the child node can be found directly
  through the array index which is the ASCII value of the target
  character. Different from other sub-types of character maps, in Map
  256, there is only one array and not necessary to carry out the
  additional indirect access. Therefore, if most entries are not
  empty, this representation is also very space efficient. Figure
  \ref{fig:character map} (d) shows a Map 256 structure, where only
  the pointer array is adopted.
\end{itemize}

@@

\begin{algorithm}
  \caption{Searching in a node whose type is character map}\scriptsize
  \label{alg:character map}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is character map\\
    The target character $t\_ch$.
    \ENSURE ~~\\
    The child node of $node.t\_ch$ (possibly $NULL$).
    \STATE
    \STATE $count \leftarrow$ Number of keys in the character map
    \STATE
    \SWITCH{the sub-type of the character map}
    \CASE{\textsf{Map 4}}
    \FOR{$i \leftarrow 0$ to $count-1$}
    \IF{$keys[i]=t\_ch$}
    \RETURN $child\_pointers[i]$
    \ENDIF
    \ENDFOR
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 16}}
    \STATE $low \leftarrow 0, high \leftarrow count-1$
    \WHILE{$low \le high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_ch=keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_ch<keys[mid]$}
    \STATE $high \leftarrow mid-1$
    \ELSE
    \STATE $low \leftarrow mid+1$
    \ENDIF
    \ENDWHILE
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 48}}
    \IF{$index[t\_ch] \neq NULL$}
    \RETURN $child\_pointers[index[t\_ch]]$
    \ELSE
    \STATE Report a mismatch.
    \ENDIF
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 256}}
    \RETURN $child\_pointers[t\_ch]$
    \ENDCASE
    \ENDPWITCH
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose length of keys is greater than 1 ($lss > 1$)
and the number of keys is not greater than 100 ($ndp \leq 100$), the
\emph{string array} structure is constructed as a tree node. Similar
to the Map 4 and Map 16 structures, the keys are stored in
lexicographical order in a separate key array of $ndp \times lss$
bytes, in which each key takes $lss$ bytes. The child pointers are
stored at the corresponding positions in another pointer array. Figure
\ref{fig:string array} illustrates a string array structure holding
three keys: $aaa$, $bbb$ and $ccc$.

@@

For efficiency, if the number of keys is less than 5, a naive linear
search routine is used to search the target string in the key array;
otherwise, a more efficient (but complicated) binary search algorithm
is adopted.  The pseudocode of the searching in a node whose type is
string array is depicted in Algorithm \ref{alg:string array}, where we
use the notation $A \prec B$ to denote that string $A$ is
\emph{lexicographically smaller} than string $B$. For the string array
whose number of keys is less than 5, the target string is compared
sequentially with the keys in the key array. If the target string
matched some key, return the child pointer at the corresponding
position in the pointer array; otherwise, report a mismatch. On the
other hand, if the number of keys is greater than 4, the target string
is searched by a binary search routine from the middle element of the
key array.

@@

For the prefix set whose number of keys is greater than 100 ($lss > 1$
and $ndp > 100$), searching in the string array structure becomes
inefficient even using a binary search. In this case, a more fast (but
heavy) data structure --- \emph{hash table} is adopted to deal with
large number of keys. It is worth noting that, the procedure of
building a hash table is directly based on the suffix set from which
the prefix set is formed rather than the prefix set which is the basis
of building other node structures. In this work, a hash table is an
array of child pointers with each pointer initialized to $NULL$, and
we also utilize a \emph{string hash function} which transforms a
string to a positive integer.

@@

Algorithm \ref{alg:hash} shows the pseudocode of building a hash table
based on $SF$. $SF$ is firstly partitioned into small suffix sets by
hashing: for each suffix $suf \in SF$, its prefix $suf^{+lss}$ is
hashed to an integer $i$ between 0 and $table\_size-1$ by the string
hash function , then $suf$ is associated with the $i$-th slot of the
hash table. After that, the suffixes whose length-$lss$ prefixes
hashing to the same value are associated with the same slot of the
hash table. Then, to address the hash collisions, for each slot that
is not $NULL$, the associated suffixes form a small suffix set $SSF$,
and a new tree node is created adaptively based on the prefix set
derived from $SSF$, as we have shown in the \textbf{while} loop of
Algorithm \ref{alg:amt}. The newly created tree node is then
associated with the corresponding slot of the hash table. As a result,
many tree nodes with various types can be associated within one hash
table.

@@

\begin{algorithm}
  \caption{Building a hash table}\scriptsize
  \label{alg:hash}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The suffix set $SF$ and the load factor $lf$. \\
    \ENSURE ~~\\
    The hash table.\\
    \STATE
    \STATE $ndp \leftarrow$ The number of distinct length-$lss$
    prefixes of suffixes in $SF$
    \STATE $table\_size \leftarrow \lceil ndp\,/\,lf \rceil$
    \STATE $hash\_table \leftarrow$ Create an array  of
    $table\_size$ pointers with each pointer initialized to $NULL$
    \STATE
    \FOR{each $suf \in SF$}
    \STATE $i \leftarrow Hash(suf^{+lss})$
    \STATE Associate $suf$ with $hash\_table[i]$
    \ENDFOR
    \STATE
    \FOR{$i \leftarrow 0$ to $table\_size - 1$}
    \IF{$hash\_table[i]\, \neq\, NULL$}
    \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
    \STATE $new\_node \leftarrow$ adaptively create a tree node from
    $SSF$, as shown in the \textbf{while} loop of Algorithm \ref{alg:amt}
    \STATE Associate $new\_node$ with $hash\_table[i]$
    \ENDIF
    \ENDFOR
    \STATE
    \RETURN $hash\_table$
  \end{algorithmic}
\end{algorithm}

Given a target string of length $lss$, the hash value of that string
is computed and used as the index of the hash table. If the
corresponding slot is $NULL$, which means the target string fails to
match any key in the hash table, the verification terminates and the
engine moves to the next position; otherwise, the process goes to the
tree node associated with that slot and compares the node with the
corresponding substring in the text.

The string hash function adopted can have a significant effect on the
performance of verifying. In our implementation, for each matching
task, the hash function is selected randomly from a \emph{hash
  function family} $H$. The hash function family adopted in our
implementation is the fast \emph{shift-add-xor} hash family proposed
by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
uniform and universal. The form of the hash function family is shown
in Algorithm \ref{alg:hash fun}.

>>>>

As stated in the filter module, once a suspicious position in the text
has been detected, the verification module checks that position for
real pattern occurrences. Specifically, for such a suspicious position
$i$, the engine searches a sequence of substrings of the text, where
the first substring starts at $i$, in the corresponding nodes of AMT
from the root. If any substring successfully matched a key that is
marked as a pattern end in some node, a pattern is declared to be
found at position $i$. However, if there is a mismatch or the
searching goes beyond the leaves of AMT, the engine immediately
forwards to the next position $i+1$ and invokes the filter again.

The pseudocode of the verification procedure is shown in Algorithm
\ref{alg:matching}. Suppose $i$ is a suspicious position of the text
detected by the filter module. The variable $m\_len$ is the total
length of the sub-strings of the text who have matched with keys in
AMT nodes. The variable $node$ points to the current searching node in
the AMT. In addition, since all the keys in a node have the same
length, the notation $key\_len(node)$ is used to denote the length of
the keys in $node$.

@@

For the suspicious position $i$, the \textbf{while} loop from line 5
to line 11 checks whether there are patterns starting at $i$. The
checking starts form the root of AMT: if the corresponding sub-string
$T[i+m\_len, \, key\_len(node)]$ matches some $key$ in the current
$node$, the totally matched length $m\_len$ is increased by the length
of the key. At the same time, if the matched $key$ is also marked as a
pattern end, the verification module will report that a pattern,
i.e. $T[i,\,m\_len]$, is found at position $i$. Then the checking
transfers to the child of $node.key$ and makes that child node to be
the current node. Once there is a mismatch or the current node goes
beyond the leaves of AMT (i.e.  $node = NULL$), the checking
terminates, and the engine forwards to the next position $i+1$.

@@

Next, an example is given in figure \ref{fig:matching} to illuminate
the verification for a suspicious position $i$ of a given text string
$T$, using the AMT built in section \ref{subsec:amt}. The verification
starts from the root of AMT: according to $key\_len(root)=2$, the same
length sub-string starting at position $i$ of $T$, which is
$T[i,\,2]=aa$, is taken to check whether it's one of the keys in
root. The result is: $aa \in root$, and $aa$ is also marked as a
pattern end. Therefore the pattern $T[i,\,2]=aa$ ($p_6$ in $P$) is
found at position $i$. Then the checking transfers to $node_1$, which
is the child node of $root.aa$.

At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
$T[i+2,\,6]=e^6$, which follows $T[i,\,2]$, is trying to match with
some key in $node_1$. The result is that: $e^6 \in node_1$ but it is
not a pattern end. Then the checking simply transfers to $node_5$,
which is the child of $node_1.e^6$.

At $node_5$, since the next sub-string $T[i+8,\,5]=u^5 \in node_5$ and
$u^5$ is marked as a pattern end, another pattern
$T[i,\,13]=a^2e^6u^5$ ($p_4$ in $P$) is found at position $i$. Then
the checking goes to the child of $node_5.u^5$, i.e.  $node_{10}$.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/Maps}
  \caption{The four sub-types of character maps. The triangles
    represent the corresponding child nodes of the keys.}
  \label{fig:character map}
\end{figure}

Figure \ref{fig:character map} illustrates the four sub-types of
character maps which are named according to their maximum
capacity. Instead of using one array of (\emph{key, child pointer})
pairs, the key part and the child pointer part are stored in the
separate arrays, which is able to keep the node structure compact
while supporting efficient search.

\begin{itemize}
\item \textbf{Map 4} (for $1 \leq ndp \leq 4$): The smallest map type
  can store up to 4 keys. It uses an array of 4 entries for keys and
  another array of the same length for child pointers. The keys and
  child pointers are stored at corresponding positions in their
  arrays, and the keys are sorted according to their ACSII
  values. Once the target character is found in the key array, its
  child pointer can be located through the same position in the
  pointer array. Figure \ref{fig:character map} (a) shows a Map 4
  structure with three keys: $f$, $n$ and $p$, where the triangles
  with the keys inside represent the corresponding child nodes.

@@

\item \textbf{Map 256} (for $49 \leq ndp \leq 256$): The largest map
  type is simply an array of 256 child pointers with each pointer
  initialized to $NULL$. It is used for storing 49 to 256 keys.  In
  this kind of character map, the child node can be found directly
  through the array index which is the ASCII value of the target
  character. Different from other character maps, in Map 256, there is
  only one array, and it is not necessary to carry out the additional
  indirect access. Therefore, if most entries are not empty, this
  representation is also very space efficient. Figure
  \ref{fig:character map} (d) shows a Map 256 structure, where only
  the pointer array is adopted.
\end{itemize}

@@

\begin{algorithm}
  \caption{Searching in a node whose type is character map}\scriptsize
  \label{alg:character map}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is character map\\
    The target character $t\_ch$.
    \ENSURE ~~\\
    The child node of $node.t\_ch$ (possibly $NULL$).
    \STATE
    \STATE $count \leftarrow$ Number of keys in the character map
    \STATE
    \SWITCH{The type of the character map}
    \CASE{\textsf{Map 4}}
    \FOR{$i \leftarrow 0$ to $count-1$}
    \IF{$keys[i]=t\_ch$}
    \RETURN $child\_pointers[i]$
    \ENDIF
    \ENDFOR
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 16}}
    \STATE $low \leftarrow 0, high \leftarrow count-1$
    \WHILE{$low \le high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_ch=keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_ch<keys[mid]$}
    \STATE $high \leftarrow mid-1$
    \ELSE
    \STATE $low \leftarrow mid+1$
    \ENDIF
    \ENDWHILE
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 48}}
    \IF{$index[t\_ch] \neq NULL$}
    \RETURN $child\_pointers[index[t\_ch]]$
    \ELSE
    \STATE Report a mismatch.
    \ENDIF
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 256}}
    \RETURN $child\_pointers[t\_ch]$
    \ENDCASE
    \ENDPWITCH
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose length of keys is greater than 1 ($lss > 1$)
and the number of keys is not greater than 100 ($ndp \leq 100$), the
\emph{string array} structure is adopted as a tree node. Similar to
the Map 4 and Map 16 structures, the keys are stored in
lexicographical order in a separate key array of $ndp \times lss$
bytes, in which each key takes $lss$ bytes. The child pointers are
stored at the corresponding positions in another pointer array. Figure
\ref{fig:string array} illustrates a string array structure holding
three keys: $aaa$, $bbb$ and $ccc$.

@@

For efficiency, if the number of keys is less than 5, a naive linear
search is used to search the target string in the key array;
otherwise, a more efficient (but complicated) binary search algorithm
is adopted.  The pseudocode of the searching in a node whose type is
string array is depicted in Algorithm \ref{alg:string array}, where we
use the notation $A \prec B$ to denote that string $A$ is
\emph{lexicographically smaller} than string $B$. For the string array
whose number of keys is less than 5, the target string is compared
sequentially with the keys in the key array. If the target string
matched some key, return the child pointer at the corresponding
position in the pointer array; otherwise, report a mismatch. On the
other hand, if the number of keys is greater than 4, the target string
is searched by a binary search routine from the middle element of the
key array.

@@

For the prefix set whose number of keys is greater than 100 ($lss > 1$
and $ndp > 100$), searching in the string array structure becomes
inefficient even using a binary search. In this case, a more fast (but
heavy) data structure --- \emph{hash table} is adopted to deal with
large number of keys. It is worth noting that, the construction of the
hash table is directly based on the suffix set from which the prefix
set is formed rather than the prefix set which is the basis of
building other node structures. In our implementation, a hash table is
an array of child pointers with each pointer initialized to $NULL$,
and we also utilize a \emph{string hash function} which transforms a
string to a positive integer.

@@

Algorithm \ref{alg:hash} shows the pseudocode of building a hash table
based on $SF$. $SF$ is firstly partitioned into small suffix sets by
hashing: for each suffix $suf \in SF$, its prefix $suf^{+lss}$ is
hashed to an integer $i$ between 0 and $table\_size-1$ by the string
hash function, then $suf$ is associated with the $i$-th slot of the
hash table. After that, the suffixes whose length-$lss$ prefixes
hashing to the same value are associated with the same slot of the
hash table. Then, to address the hash collisions, for each slot that
is not $NULL$, the associated suffixes form a small suffix set $SSF$,
and a new tree node is created adaptively based on the prefix set
derived from $SSF$, as we have shown in the \textbf{while} loop of
Algorithm \ref{alg:amt}. The newly created tree node is then
associated with the corresponding slot of the hash table. As a result,
many tree nodes with various types can be associated within one hash
table.

@@

\begin{algorithm}
  \caption{Building a hash table}\scriptsize
  \label{alg:hash}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The suffix set $SF$ and the load factor $lf$. \\
    \ENSURE ~~\\
    The hash table.\\
    \STATE
    \STATE $ndp \leftarrow$ The number of distinct length-$lss$
    prefixes of suffixes in $SF$
    \STATE $table\_size \leftarrow \lceil ndp\,/\,lf \rceil$
    \STATE $hash\_table \leftarrow$ Create an array  of
    $table\_size$ pointers with each pointer initialized to $NULL$
    \STATE
    \FOR{each $suf \in SF$}
    \STATE $i \leftarrow Hash(suf^{+lss})$
    \STATE Associate $suf$ with $hash\_table[i]$
    \ENDFOR
    \STATE
    \FOR{$i \leftarrow 0$ to $table\_size - 1$}
    \IF{$hash\_table[i]\, \neq\, NULL$}
    \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
    \STATE $new\_node \leftarrow$ Adaptively create a tree node from
    $SSF$, as shown in the \textbf{while} loop of Algorithm \ref{alg:amt}
    \STATE Associate $new\_node$ with $hash\_table[i]$
    \ENDIF
    \ENDFOR
    \STATE
    \RETURN $hash\_table$
  \end{algorithmic}
\end{algorithm}

Given a target string of length $lss$, the hash value of that string
is computed and used as the index of the hash table. If the
corresponding slot is $NULL$, which means there is a mismatch, the
verification terminates and the engine moves to the next position;
otherwise, the process goes to the tree node associated with that slot
and compares the node with the corresponding substring in the text.

The string hash function adopted can have a significant effect on the
performance of verifying. In our implementation, for each matching
task, the hash function is selected randomly from a \emph{hash
  function family} $H$. The hash function family adopted in our
implementation is the fast \emph{shift-add-xor} hash family proposed
by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
uniform and universal. The framework of the hash function family is
shown in Algorithm \ref{alg:hash fun}.
